---
title: "Covid Tracker"
output: 
  flexdashboard::flex_dashboard:
    logo: "this_PP_znak.png"
    orientation: rows
    vertical_layout: fill
    source_code: embed
    theme: cosmo
runtime: shiny
---

```{r global, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(knitr)
library(ggiraph)
library(plotly)
library(highcharter)
library(googleVis)
library(metricsgraphics)
library(viridis)
library(DT)
library(readr)
library(RCurl)
library(rio)
data <- rio::import("https://raw.githubusercontent.com/allsuitablenamesarealreadytaken/Covid-Tracker-dashboard/main/superNewData.csv",
                    format = "csv")
```
Sidebar {.sidebar}
=======================================================================
 
```{r}
selectInput('selected_country', 'Select Country', unique(data["location"]))
```

Map
=======================================================================

Row
-----------------------------------------------------------------------

### Total cases around the world

```{r}
un <- unique(data[["location"]])
countries <- character(length(un))
means <- numeric(length(un))
  
for (x in 1:length(un)){
  check <- max(data[data["location"] == un[x], ]["total_cases"], na.rm = TRUE)
  if(is.infinite(i<-suppressWarnings(check))){
    countries[x] <- un[x]
    means[x] <- 0
  }
  else{
    if(check < 50000000){
        countries[x] <- un[x]
        means[x] <- as.numeric(check)
    }
  }
}
  
dt <- data.frame(countries, means)
  
hc <- highchart() %>%
  hc_add_series_map(
    map=worldgeojson, df=dt, value = "means", joinBy = c('name', 'countries'),
    name = "Cases"
  )  %>% 
  hc_colorAxis(minColor = "cornflowerblue", maxColor = "lightcoral") %>% 
  hc_title(text = "World Map") %>% 
  hc_subtitle(text = "Total cases")
  
hc
```

### General data

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})

DT::renderDataTable({
  DT::datatable(selectedData(), extensions = 'Buttons', options = list(dom = 'Brtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'), 
                lengthMenu = list(c(10,25,50,-1), c(10,25,50,"All"))))
})
```


Statistics
=======================================================================

Row
-----------------------------------------------------------------------

### People vaccinated {.value-box}

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})

renderValueBox({
  people_vaccinated <- max(selectedData()["people_vaccinated"], na.rm = TRUE)
  if(is.infinite(x<-suppressWarnings(people_vaccinated))){
    people_vaccinated <- "No Data"
  }
  valueBox(
    value = people_vaccinated,
    icon = "fa-users",
    color = "success"
  )
})
```

### Total tests

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})

renderValueBox({
  total_tests <- max(selectedData()["total_tests"], na.rm = TRUE)
  if(is.infinite(x<-suppressWarnings(total_tests))){
    total_tests <- "No Data"
  }
  valueBox(
    value = total_tests,
    icon = "ion-android-checkmark-circle",
    color = "primary"
  )
})
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Total cases {.tabset .tabset-fade}

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})


renderPlotly({
  total_cases <- selectedData()["total_cases"]
  dates <- selectedData()["date"]
  total <- data.frame(total_cases, dates)
  
  scatter_ggplot <- ggplot(total, aes(x = as.Date(date, "%Y-%m-%d"), y = total_cases, color = total_cases, 
    text = paste('</br> Date: ', date, '</br> Total cases: ', total_cases))) +
    geom_point(alpha = 0.25) +
    scale_color_viridis() +
    labs(x="Dates", y="Number of total cases") +
    theme_minimal() +
    theme(legend.position="none", text = element_text(size=17))
  
  ggplotly(scatter_ggplot, hoverinfo = "none")
  
})
```

### New cases {.tabset .tabset-fade}

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})

renderPlot({
  twenty <- selectedData()[selectedData()["year"] == 2020, ]
  twenty <- na.omit(twenty["new_cases"])
  one <- selectedData()[selectedData()["year"] == 2021, ]
  one <- na.omit(one["new_cases"])
  two <- selectedData()[selectedData()["year"] == 2022, ]
  two <- na.omit(two["new_cases"])
  years <- c("2020", "2021", "2022")
  means <- c(mean(twenty[, "new_cases"]), mean(one[, "new_cases"]), mean(two[, "new_cases"]))
  new_cases <- data.frame(years, means)
  ggplot(new_cases, aes(x=years, y=means)) + geom_bar(stat="identity", width=0.5, fill='cornflowerblue') + 
  labs(x="Years", y="Number of cases") +
  theme_minimal() +
  theme(legend.position="none") + theme(text = element_text(size=17))
})

```

### Deaths {.tabset .tabset-fade}

```{r}
selectedData <- reactive({
  data[data["location"] == input$selected_country, ]
})

renderPlot({
   twenty2 <- selectedData()[selectedData()["year"] == 2020, ]
   twenty2 <- na.omit(twenty2["total_deaths"])
   one2 <- selectedData()[selectedData()["year"] == 2021, ]
   one2 <- na.omit(one2["total_deaths"])
   two2 <- selectedData()[selectedData()["year"] == 2022, ]
   two2 <- na.omit(two2["total_deaths"])
   years2 <- c("2020", "2021", "2022")
   means2 <- c(mean(twenty2[, "total_deaths"]), mean(one2[, "total_deaths"]), mean(two2[, "total_deaths"]))
   new_cases2 <- data.frame(years2, means2)
   ggplot(new_cases2, aes(x=years2, y=means2)) + geom_bar(stat="identity", width=0.5, fill='lightcoral') + 
   labs(x="Years", y="Number of deaths") +
   theme_minimal() +
   theme(legend.position="none") + theme(text = element_text(size=17))
})
```

About
=======================================================================


<style type="text/css">
body{ /* Normal  */
      font-size: 15px;
}
h4 { /* Header 4 */
  font-size: 35px;
  color: DarkBlue;
}
</style>

Row
-----------------------------------------------------------------------

#### Covid-19 and us <br/> <br/> Since the report of the first cases of pneumonia caused by SARS-CoV-2 in December 2019, COVID-19 has become a pandemic and is globally overwhelming healthcare systems. <br/> The symptoms of COVID-19 vary from asymptomatic infection to severe complicated pneumonia with acute respiratory distress syndrome (ARDS) and multiple organ failure leading to death. <br/> The estimated case-fatality rate among infected patients in Wuhan, the city where the first case appeared, was 1.4%, with 5.1 times increase in the death rate among those aged above 59 years than those aged 30–59 years. <br/> In the absence of a proven effective and licensed treatment, many agents that showed activity against previous coronavirus outbreaks such as SARS and MERS have been used to treat SARS-CoV-2 infection. <br/> The SARS-CoV-2 is reported to be 80% homologous with SARS-CoV, and some enzymes are almost 90% homologous. <br/> Antiviral drugs are urgently required to reduce case fatality-rate and hospitalizations to relieve the burden on healthcare systems worldwide. <br/> Randomized controlled trials are ongoing to assess the efficacy and safety of several treatment regimens. <br/> <br/> Unfortunately, most of us can relate to this world-wide issue we have to deal with on daily basis. <br/> Due to that, it was important for us to create a resourse accessible for everyone. It shows the Covid-19 related data about a country selected by a user. Convenient navigation helps a user get the information their want effortlessly. <br/> <br/> Enjoy!
